\section*{Mission Statement}
My mission is to write software which \emph{kicks ass}.  I want to work with
smart and creative people on projects which are worth doing right, help people
in creative ways, and improve the computer's role as a cognitive tool.  I am
especially interested in geography, artificial intelligence, human language,
cognitive science, and programming languages.
\section*{Computer Nerd}
  \begin{compactitem}
    \item 
    Since my introduction to Logo and BASIC at age 10, I have relished wrapping
my mind around formal language and precise instructions.  My professional coding
experience lies mostly in Java and JavaScript. In my quest for the right
balance between fluid English and mathematical formalism I've dabbled in many
languages, with C, Ruby, Perl, Python, Go, and Lisp among those I've taken a
liking to.
    \item 
    A distant descendant of \emph{Homo habilis}, I adapt quickly to new
environments and tools. I swim comfortably in Linux and Mac environments. I pen
code in Eclipse and vim. I speak standards like html, css, sql, and xml.
    \item
    Since 2009 I've worked as a software engineer at Google, Inc.  I work on
Google Docs, helping millions of users organize, share, and enjoy their
documents and files. Using Java, JavaScript, and internal tools I have built
new features, improved legacy code, monitored production services, and gathered
statistics on usage.
    \item 
    From 2004 to 2009 I worked as a software engineer at Tyler Technologies, Inc.
I worked at all levels of their Java-based enterprise applications.  I explored
and questioned requirements with analysts, built Swing-based GUIs, designed core
services, refactored key data structures, debugged the persistence layer, led
complex module development, crafted a data conversion specification, and
reviewed almost every commit. I created a system to
extract named entities from OCR text. I developed the architecture and user
interface to work with GIS data. I stood out as a ``go-to-guy'' for insight
about everything from subsystem design to text processing.
    \item 
    At UNAVCO, Inc.~in 2003 I used Perl and JavaScript to create
educational Earth science map tools.
    \item 
    In December, 2003 I graduated from the University of Colorado, Boulder.  I
received both a Bachelor of Science With Distinction and a Master of Science in
Computer Science.  My GPA was 3.8 on a 4.0 scale.
    \item 
    I pursued advanced coursework in object oriented design, algorithms,
programming languages, operating systems, network systems, cognitive science,
artificial intelligence, machine learning, speech recognition, natural language
processing, user interface design, network systems, and Unix system administration.
  \end{compactitem}
\section*{Eclectic Philosopher}
  \begin{compactitem}
    \item At CU, I minored in philosophy and was president of the Philosophy Club.
I love to explore life's deep questions.  I use analytic and holistic techniques
to explore ethics, society, identity, and metaphysics.  I presented a paper on
weakness of will at the 2002 Rocky Mountain Student Philosophy Conference.
    \item During high school I taught a Socratic seminar course on world philosophy.
    \item My world view ties computer science to philosophy and psychology.  I am
fascinated by artificial intelligence, cognitive science, linguistics, limits of
formal systems, self-organization, and societal use of computers.
  \end{compactitem}
\section*{Generally Diverse Individual}
  \begin{compactitem}
    \item My calm personality, helpful demeanor, mediation and problem solving
skills, and concern for public safety led me to positions as a resident advisor
at CU and a Black Rock Ranger at Burning Man.
    \item In college, I developed leadership skills as chapter vice president of
Tau Beta Pi, the national engineering honor society, and as organizer of Pagan
and Green Party student groups.
    \item I am a friendly and unique individual.  While I take projects and tasks
seriously, a subtle wit and creative approach to the mundane pervade my actions,
keeping a smile present among my fellows. My extensive knowledge of geographic,
historic, and scientific facts entertains coworkers during casual moments.
    \item I love language.  I play with English idioms, speak passable
Spanish, and dabble in Chinese.
    \item I connect with the world around me through photography, camping, 
bicycling, and playing games.
  \end{compactitem}
